Footpath Planning for Example-driven Procedural Road Networks

### 2020-03-13 paper/paper.tex
Update paper with info on SLU data and coordinate system

\begin{multicols}{2}

@@

@@

\end{multicols}

\begin{thebibliography}{9}
\bibitem{sampleitem1}
Title 1, \\ 
\href{https://en.wikipedia.org/wiki/Geostationary\_ orbit}{https://en.wikipedia.org/wiki/Geostationary\_ orbit}.

\bibitem{sampleitem2}
Title 2, \\ 
\href{https://sv.wikipedia.org/wiki/SpaceX}{https://sv.wikipedia.org/wiki/SpaceX}.

>>>>

@@

\subsection(SLU Data)

The SLU map is maintained by The Swedish National Land Survey (Swedish: Lantmäteriet).
The SLU data is aqqcuired by land surveying methods such as GPS or DGNSS positioning, or by reproduction of features from ortophoto or stereo mapping from 3D aerial images.
The map is updated continously by Lantmäteriet, in conjoncture with the forming or reforming of property.
Property limits and building features have a position accuracy requirement of 5 meters.
(Lantmäteriet, 2019)

\subsection(A word on coordinate systems)

The SLU dataset comes in the SWEREF 99 TM (Lantmäteriet, 2019). SWEREF 99 TM is a projected coordinate system and there is no linear transformation to WGS 48, which OpenStreetMap uses (OSM 19). The coordinate conversions for this paper were obtained using proj: a Linux commandline application for geospatial coordinate conversion.

@@

\begin{thebibliography}{9}

\bibitem{lantmateriet-19}
(Lantmäteriet, 2019), Produktbeskrivning: GSD-Fastighetskartan vektor \\ 
\href{https://www.lantmateriet.se/globalassets/kartor-och-geografisk-information/kartor/fastshmi.pdf}.

\bibitem{osm-19}
(OSM 19) Converting to WGS84, accessed 13-03-2020\\ 
\href{https://wiki.openstreetmap.org/wiki/Converting_to_WGS84}.
